A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-24 doc/Paper1/ms.tex
Cleaning up

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_2$	&	Time delay of image 2	&	Cauchy$\left(0, 0.1\tau_{\rm range}\right)T\left(\tau_{\rm min},\tau_{\rm max}\right)$\\
$\{m_1, m_2\}$	&	Mean magnitude for each image	& Uniform$(m_{\rm min}, m_{\rm max})$\\
$\beta$		&	Size of QSO variations		& LogUniform$(\beta_{\rm min}, \beta_{\rm max})$\\
$L$		&	Length scale of QSO variations	& LogUniform$(L_{\rm min}, L_{\rm max})$\\
$\{S_1, S_2\}$	&	Size of image-specific variations	& LogUniform$\left(A_{\rm min}, A_{\rm max}\right)$\\
$\{\ell_1, \ell_2\}$ &	Length scale of image-specific variations & LogUniform$(\ell_{\rm min}, \ell_{\rm max})$\\
$\alpha$	&	Smoothness of image-specific variations	& Uniform$(1, 2)$\\
$f_{\rm bad}$	&	Fraction of ``bad'' data points	& Uniform$(0,1)$\\
$\kappa_1$	&	Error-bar boost for ``good'' data & $\frac{1}{2}\delta(\kappa_1 - 1) + \frac{1}{2}$LogUniform$(1,100)$\\
$\kappa_2$	&	Error-bar boost for ``bad'' data & LogUniform$(\kappa_1, 100\kappa_1)$\\
$\{b_i\}_{i=1}^N$ &	Badness hidden variables for each data point & Uniform$(0,1)$\\
\hline
{\bf Derived Parameter} & {\bf Meaning}	&	{\bf Definition}\\
\hline
$S_{\rm QSO}$	&	Standard deviation of QSO variability	& $\beta\sqrt{L}$\\
$\{B_i\}_{i=1}^N$	&	Badness flag for each data point & $\mathds{1}\left(b_i \leq f_{\rm bad}\right)$\\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\caption{A full list of parameters, prior information, and data in the
FLOTSAM model. If there are more than two images, extra parameters are
added accordingly.\label{tab:prior}}
\end{table*}

@@

We assume that the covariance function for the quasar variability is given by
\begin{eqnarray}
\textnormal{Cov}\left[f(t_1), f(t_2)\right] = C(|t_2 - t_1|)
\end{eqnarray}
where
\begin{eqnarray}
C(\Delta t) = \sigma_{\rm QSO}^2\exp\left(-\frac{\Delta t}{L_{\rm QSO}}\right)
\end{eqnarray}

{\bf COMMENT ON KELLY}

Similarly, the covariance function for each of the microlensing components is
\begin{eqnarray}
\textnormal{Cov}\left[\mu(t_1), \mu(t_2)\right] = C_{\rm micro}(|t_2 - t_1|)
\end{eqnarray}
where
\begin{eqnarray}
C_{\rm micro}(\Delta t) = \sigma_{\rm micro}^2\exp\left(-\left(\frac{\Delta t}{L_{\rm micro}}\right)^{\alpha_{\rm micro}}\right)
\end{eqnarray}

There is a $\sigma_{\rm micro}$  parameter and an $L_{\rm micro}$ parameter
for each image; this is because the stellar density and lens convergence is
different at each image position. In contrast, we use a single $\alpha_{\rm
micro}$ parameter for all images; this is because it is suspected that the
smoothness of the microlensing variations, which $\alpha$ describes, depends
primarily on the size of the microlensed source, and all images are of the
same source.

>>>>

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_2$	&	Time delay of image 2	&	Cauchy$\left(0, 0.1\tau_{\rm range}\right)T\left(\tau_{\rm min},\tau_{\rm max}\right)$\\
$\{m_1, m_2\}$	&	Mean magnitude for each image	& Uniform$(m_{\rm min}, m_{\rm max})$\\
$\beta$		&	Size of QSO variations		& LogUniform$(\beta_{\rm min}, \beta_{\rm max})$\\
$L_q$		&	Length scale of QSO variations	& LogUniform$(L_{\rm min}, L_{\rm max})$\\
$\{S_1, S_2\}$	&	Size of image-specific variations	& LogUniform$\left(A_{\rm min}, A_{\rm max}\right)$\\
$\{\ell_1, \ell_2\}$ &	Length scale of image-specific variations & LogUniform$(\ell_{\rm min}, \ell_{\rm max})$\\
$\alpha$	&	Smoothness of image-specific variations	& Uniform$(1, 2)$\\
$f_{\rm bad}$	&	Fraction of ``bad'' data points	& Uniform$(0,1)$\\
$\kappa_1$	&	Error-bar boost for ``good'' data & $\frac{1}{2}\delta(\kappa_1 - 1) + \frac{1}{2}$LogUniform$(1,100)$\\
$\kappa_2$	&	Error-bar boost for ``bad'' data & LogUniform$(\kappa_1, 100\kappa_1)$\\
$\{b_i\}_{i=1}^N$ &	Badness hidden variables for each data point & Uniform$(0,1)$\\
\hline
{\bf Derived Parameter} & {\bf Meaning}	&	{\bf Definition}\\
\hline
$S_{q}$	&	Standard deviation of QSO variability	& $\beta\sqrt{L}$\\
$\{B_i\}_{i=1}^N$	&	Badness flag for each data point & $\mathds{1}\left(b_i \leq f_{\rm bad}\right)$\\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\caption{A full list of parameters, prior information, and data in the
FLOTSAM model. If there are more than two images, extra parameters are
added accordingly.\label{tab:prior}}
\end{table*}

@@

We model our uncertainties about the underlying QSO light curve $q(t)$ by
a GP with mean function $\mathds{E}\left(q(t)\right) = 0$ and covariance function
\begin{eqnarray}
\textnormal{Cov}\left[q(t_1), q(t_2)\right] = S_q\exp
\left[-\frac{|t_2 - t_1|}{L_q}\right]
\end{eqnarray}

This model for QSO variability has been studied extensively by \citep{}
{\bf COMMENT ON KELLY}. We also note that this distribution is a MaxEnt
distribution \citep{} with XX constraints \citep{sivia}.

Similarly, our uncertainty about the image-specific variability is modelled
as a GP with mean function $\mathds{E}\left(\mu_i(t)\right) = 0$ and
covariance function
\begin{eqnarray}
\textnormal{Cov}\left[\mu_i(t_1), \mu_i(t_2)\right] =
S_i\exp\left[
-\left(\frac{|t_2 - t_1|
}{\ell_i}\right)^\alpha
\right]
\end{eqnarray}

There is a separate $S_i$ parameter $\ell_i$ parameter
for each image; this is because the stellar density and lens convergence is
different at each image position. If the image-specific variability is
predominantly caused by microlensing, the typical timescales and amplitudes
of the microlensing are unlikely to be the same for each image.
In contrast, we use a single $\alpha$ parameter for all images;
this is because it is suspected that the
smoothness of the microlensing variations, which $\alpha$ describes, depends
primarily on the size of the microlensed source, and all images are of the
same source.
